The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-30 design.tex
add mode diagrams and rebuild the structure

\subsubsection{Master plan} % (fold)
\label{ssub:master_plam}
With the cloud manufacturing platform operating, demander comes, signs up and publish orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations. Match module in platform informs the task messages to every matched resources and services. After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before. Most of resource related decision making are well controlled by platform with the review module.

A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform. While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity of $C_k(\tau)$ at any point in time $\tau$.

A single service($s_l$) is a composition of all resources in set $R_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more. While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
% \begin{table}[htbp]
%   \centering
%   \scriptsize
%   \caption{Simple resource configuration}
%     \begin{tabular}{ccc}
%     \toprule
%     Resource & Type  & Capacity \\
%     \midrule
%     $r_1$ & 1     & 10 \\
%     $r_2$ & 2     & 10 \\
%     $r_3$ & 3     & 10 \\
%     $r_4$ & 3     & 10 \\
%     \bottomrule
%     \end{tabular}%
%   \label{tab:simpleresourceconfiguration}%
% \end{table}%
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

\subsubsection{Assumptions, nomenclature} % (fold)
\label{ssub:assumptions_nomenclature}
Assumptions about quality

@@

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

For the continuous coming of provider, demander, order, task, etc., the amount of them can not be determined at any time point, so we doesn't restrict the upper bound for subscript index amount of all these variables, and we will study the decision separately for these individual at the given time point $\tau$. Detailed design will be explained in the following sections.
% subsubsection assumptions_nomenclature (end)
% subsection preliminaries (end)

\subsection{Interactions and decisions} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Demander}
\label{subs:Demander}
Demander makes decision about resources and services selection for the task. Without loss of generalization, we suppose at time period $\tau$, demander received bunch of matched resource and services as candidates for the performance of the published order $o_i$, it's obvious that $\tau \ge r_{i}$. The decision making for any task included in $o_i$, let's take $t_{ij}$, can be described in one of the following 3 situation:

\begin{asparaenum}
\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
\suspend{asparaenum}
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & 
\end{numcases}

@@

\subsubsection{Provider}
\label{subs:Provider}
Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call. As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks. Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:

\subsection{Operation mode} % (fold)
\label{sub:operation_mode}
The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure. Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:
\begin{asparaenum}
\item Assign new task $t_{ij}$ in $mr_k$.
\suspend{asparaenum}

@@

\resume{asparaenum}
\item Assign new service-call $sc_l$ in $mr_k$.
\suspend{asparaenum}

@@

\resume{asparaenum}
\item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
\suspend{asparaenum}

@@

@@

\resume{asparaenum}
\item Outsource the task in both active and inactive status.
\end{asparaenum}

@@

For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status will decrease. This decision highly depends on the estimate of performance status in other resources and services.

\subsection{Controlling rules} % (fold)
\label{sub:controlling_rules}
The decision makings explained above are controlled by review and ranking mechanism provided by platform, the provider who have higher rank value will be safer to stay in the ecosystem, have more chance to succeed in generating services, his services and resources will get more preference. Hence, here we will explain some controlling rules related to the rank value changing:
\begin{asparaenum}
\item Review from demander when his task $t_{ij}$ was finished by resource cooperation $mr_{\bm{k}}$:
\suspend{asparaenum}

@@

\subsection{Tricky problems} % (fold)
\label{sub:tricky_problems}
Even though the schedule mode exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed. Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock}, 
\begin{figure}[htbp]
	\centering
	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
	\caption{Simple illustration of job lock problem}
	\label{fig:joblock}
\end{figure}
$t_{i2}$ is active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is active in $mr_1$ and inactive in $mr_2$, because of the capacity limit, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and will they will block the other tasks from being processed.

>>>>

\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Origin mode}
    \label{fig:originmode}
\end{figure}

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
Assumptions about quality

@@

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

For the continuous coming of provider, demander, order, task, etc., the amount of them can not be determined at any time point, so we doesn't restrict the upper bound for subscript index amount of all these variables, and we will study the decision separately for these individual at the given time point $\tau$. Detailed design will be explained in the following sections.
% subsubsection assumptions_nomenclature (end)
\subsubsection{Master plan} % (fold)
\label{ssub:master_plam}

A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform. While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$.

% subsection preliminaries (end)

\subsection{Individual decisions and ecosystem mode options} % (fold)
\label{sub:interactions_and_decisions}

\subsubsection{Selection in resource candidates}
\label{subs:Demander}
Demander makes decision about resources and services selection for the task. Without loss of generalization, we suppose at time period $\tau$, demander received bunch of matched resource and services as candidates for the performance of the published order $o_i$, it's obvious that $\tau \ge r_{i}$. The decision making for any task included in $o_i$, let's take $t_{ij}$, can be described in one of the following 3 situation:

\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & 
\end{numcases}

\subsubsection{Response in selected resource}
\label{subs:Provider}
Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call. As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks. Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure. Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:

A single service($s_l$) is a composition of all resources in set $\bm{mr}_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more. While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.

\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Service incubate mode}
    \label{fig:serviceincubatemode}
\end{figure}

\begin{asparaenum}
\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
\suspend{asparaenum}

@@

\begin{asparaenum}
\item Assign new task $t_{ij}$ in $mr_k$.
\suspend{asparaenum}

@@

\resume{asparaenum}
\item Assign new service-call $sc_l$ in $mr_k$.
\end{asparaenum}

@@

% \resume{asparaenum}
% \item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
% \suspend{asparaenum}

% \resume{asparaenum}
% \item Outsource the task in both active and inactive status.
% \end{asparaenum}

\subsection{Schedule the jobs in machine} % (fold)
\label{sub:schedule_the_jobs_in_machine}

@@

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.

\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

% subsection schedule_the_jobs_in_machine (end)

\subsection{Outsource mode} % (fold)
\label{sub:outsource_mode}

\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
    \caption{Outsource mode}
    \label{fig:outsourcemode}
\end{figure}

@@

For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status will decrease. This decision highly depends on the estimate of performance status in other resources and services.
% subsection outsource_mode (end)

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}

\begin{figure}[htbp]
    \centering
    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
    \caption{Metabolism mode}
    \label{fig:metabolismmode}
\end{figure}
The decision makings explained above are controlled by review and ranking mechanism provided by platform, the provider who have higher rank value will be safer to stay in the ecosystem, have more chance to succeed in generating services, his services and resources will get more preference. Hence, here we will explain some controlling rules related to the rank value changing:
\begin{asparaenum}
\item Review from demander when his task $t_{ij}$ was finished by resource cooperation $mr_{\bm{k}}$:
\suspend{asparaenum}

@@

\subsection{Tricky problem} % (fold)
\label{sub:tricky_problems}
Even though the schedule mode exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed. Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock}, 
\begin{figure}[htbp]
	\centering
	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
	\caption{Simple illustration of job lock problem}
	\label{fig:joblock}
\end{figure}
$t_{i2}$ is active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is active in $mr_1$ and inactive in $mr_2$, because of the capacity limit, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and will they will block the other tasks from being processed.

### 2016-08-30 figures/origin_mode.tex
add mode diagrams and rebuild the structure

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=-1em,column sep=2em] {
% First row:
\node (order) {Order};& \node (task) [square]{Publish Tasks}; & & & & \\
 & &\node (match) [square]{Match \& Assign};&\node (coord) [square] {Resource Cooperate}; & \node (process)[square]{Process Task}; & \node (finish) {Product};\\
\node (provider) {Provider}; & \node (resource) [square]{Provider Resources}; & & & & \\
};
\path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
% \path (task) edge[->] (job);
% \node (ui1) [nonterminal] {unsigned integer};
% \node (dot) [terminal,right=of ui1] {.};
% \node (digit) [terminal,right=of dot] {digit};
% \node (E) [terminal,right=of digit] {E};
% \node (plus) [terminal,above right=of E] {+};
% \node (minus) [terminal,below right=of E] {-};
% \node (ui2) [nonterminal,below right=of plus] {unsigned integer};
\end{tikzpicture}

>>>>

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start) {}; & & & & & & \node (stop) {}; \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (candidate) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (coord) [square] {Cooperate \& Process};&\\
};
\draw[dotted,thick] (start.west) -- (stop.east);
\path (task) edge[->,dashed] (response) (response) edge[->] (candidate) (candidate) edge[->] (select) (select) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (finish);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

### 2016-08-30 intro.tex
start to study the operation model
describe operation model and microscopic evolution
添加新条目
re structure
main content finished
change without design.tex
start to draw diagram
add mode diagrams and rebuild the structure

% !Mode:: "TeX:UTF-8"
% !TEX root = Eco-Model.tex
\section{test}

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
With the emergence of cloud manufacturing, the relationship among participants in the manufacturing system become more complicated then ever before since every single ind

In this paper, we constructed a

proposed 3 operation modes as options for platform to operate with named metabolism mode, incubation mode and outsourcing mode.

### 2016-08-30 review.tex
add mode diagrams and rebuild the structure

>>>>

With the cloud manufacturing platform operating, demander comes, signs up and publish orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations. Match module in platform informs the task messages to every matched resources and services. After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before. Most of resource related decision making are well controlled by platform with the review module.
